Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements

### 2025-03-29 Submission.Rmd
tried applying vancouver style
updating paper

---
title             : "Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements"
shorttitle        : "O*NET JD-R"

@@

## The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework

Two related theories serve as the foundation for the current study: the job demands-resources theory [e.g., @bakker2014job; @bakker2017job] and @cavanaugh2000empirical's challenge-hindrance stressor framework. The job demands-resources theory [e.g., @bakker2014job; @bakker2017job] highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job]. The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Both are considered stressors/demands [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

@@

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).

@@

## Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?

@@

Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework. In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p. 3). They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].

@@

The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \@ref(fig:ourmodel) for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

@@

@@

@@

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics. For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

Of the `r nrow(use)` individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless]. Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample. Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years. Respondent ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (*SD* = `r round(sd(data[,403], na.rm=TRUE),2)`). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).

The Occupational Information Network (O\*Net) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding]. The O\*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated. We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

@@

@@

The findings presented above have implications for both theory and practice. First, this research is situated within the familiar job demands-resources theory [@demerouti2001job]. Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics. In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending]. This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical]. Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical], which we partially supported here.

@@

In sum, this endeavor builds on the job-demands-resources, and challenge-hindrance stressor literature from a unique lens from within a universally accessible framework. We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests. While resources and challenges were more similarly experienced, what is experienced as a hindrance tends to be more variable. We further provide additional evidence highlighting the value of perceived resources in the workplace, as they were demonstrated to moderate both challenge-engagement, and hindrance-stress/hindrance burnout relationships.

>>>>

---
title             : "Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements"
shorttitle        : "O*NET JD-R"

@@

## The Challenge-Hindrance Stressor Framework

@cavanaugh2000empirical's challenge-hindrance stressor framework serves as the theoretical foundation for this work. First, *resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job]. The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job). 
@cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

@@

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement), although there have been criticisms of this framework [e.g., @mazzola2019should; @kubicek2023all].

@@

@@

Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework. In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p. 3). They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].

@@

IS THIS TOO CLOSELY TIED TO THE JOB DEMANDS RESOURCES THEORY? CHECK

The second set of predictions focus on associations with theory-relevant outcomes of the challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \@ref(fig:ourmodel) for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

@@

AGAIN, CHECK TO SEE IF THIS IS TOO CLOSELY ALIGNED WITH JDR RATHER THAN CHALLENGE-HINDRANCE

@@

The final usable sample consisted of `r nrow(data)`. Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years. Respondent ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (*SD* = `r round(sd(data[,403], na.rm=TRUE),2)`). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).

Characteristics, Challenge Demands, Hindrance Demands, and Resources. The Occupational Information Network (O\*Net) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding]. The O\*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated. We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

Participants were asked to think about whether or not their job could be described as consisting of 98 different O\*Net job characteristics. For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

Stress. Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time. A sample item is, “How often have you had problems relaxing because of your job?”. Obtained alpha was .85 in this sample.

Burnout. Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout. Again, responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time. A sample item is, “How often have you felt worn out?”. Alpha was 0.85 in this sample.

Engagement. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample 𝛼’s of
0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication). Responses were provided using a Likert-type scale ranging from (1) Strongly Disagree to (6) Strongly Agree. A sample item is, “I enjoy thinking about work even when I'm not at work”. For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).

@@

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

@@

Of the `r nrow(use)` individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless]. Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample.

@@

The findings presented above have implications for both theory and practice. our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending]. This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical]. Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical], which we partially supported here.

@@

In sum, this endeavor builds on the challenge-hindrance stressor literature from a unique lens from within a universally accessible framework. We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests. While resources and challenges were more similarly experienced, what is experienced as a hindrance tends to be more variable. We further provide additional evidence highlighting the value of perceived resources in the workplace, as they were demonstrated to moderate both challenge-engagement, and hindrance-stress/hindrance burnout relationships.
